\documentclass{mycv}

\name{Goujin Chen}
\address{Department of Computer Science \\ The Chinese University of Hong Kong, Hong Kong}
\email{cgjhaha@qq.com}
\homepage{https://github.com/dekura}
\github{dekura}
\linkedin{dekura}

\begin{document}

\maketitle%

\section{Research \\ Interests}

I am interested in Machine Learning, EDA, VLSI design. My current focuses include:

\begin{itemize}
  \item Machine Learning in VLSI Design.
\end{itemize}

\section{Professional \\ Experience}

\subsection{Simon Fraser University}[Burnaby, BC, Canada]
\begin{positions}
  \entry{Visiting Scholar}{Mar 2020~--~Present}
\end{positions}

\begin{itemize}
  \item Advisor: \href{https://www.cs.sfu.ca/~jpei/}{Prof.~Jian Pei}
  \item Designing novel techniques to build future generation high performance blockchain systems.
  \item Developing a prototype to demonstrate the effectiveness of the proposed system.
\end{itemize}

\subsection{Hong Kong Baptist University}[Hong Kong]
\begin{positions}
  \entry{Ph.D.\ Candidate}{Nov 2014~--~Feb 2019}
  \entry{Senior Research Assistant / Post-doctoral Research Fellow}{Dec 2018~--~Present}
\end{positions}

\begin{itemize}
  \item Advisor: \href{https://www.comp.hkbu.edu.hk/~xujl}{Prof.~Jianliang Xu}
  \item Designed novel algorithms and indexes for cloud-based query services to support efficient verifiable query processing in a wide range of enterprise systems.
  \item Developed novel techniques to enable integrity assured search in blockchain databases.
  \item Resulted to several research papers published in top-tier journals and conferences.
\end{itemize}

\subsection{Syracuse University}[Syracuse, NY, USA]
\begin{positions}
  \entry{Visiting Scholar}{Sep 2017~--~Dec 2017}
\end{positions}

\begin{itemize}
  \item Advisor: \href{https://tristartom.github.io}{Dr.~Yuzhe Tang}
  \item Designed and implemented a memory-access pattern secure software system on Intel SGX\@.
  \item Developed a dynamic program partitioning framework to support implementing a variety of external oblivious algorithms and achieving cache-miss obliviousness.
\end{itemize}

\subsection{Homebrew}[Hong Kong]
\begin{positions}
  \entry{Core Maintainer}{Feb 2015~--~Feb 2017}
\end{positions}

\begin{itemize}
  \item \url{https://brew.sh}
  \item Acted as one of the core maintainers for the open source project Homebrew, which is the most popular package manager on macOS\@.
  \item Implemented several major features and improvements including better tap system, core/formulae split, sandbox system, portable Ruby, and many bug fixes.
\end{itemize}

\section{Education}

\subsection{The Chinese University of Hong Kong}[Hong Kong]
\begin{positions}
  \entry{Ph.D. \ in Computer Science}{Nov 2021~--~Feb 2024}
\end{positions}
\vspace{-\parskip}%
\begin{itemize}
  % \item Ph.D.\ in Computer Science \printdate{Nov 2021~--~Feb 2024}
  % \item Dissertation: \href{https://repository.hkbu.edu.hk/etd_oa/620}{Authenticated Query Processing in the Cloud}
  \item Advisor: \href{http://www.cse.cuhk.edu.hk/~byu/}{Prof.~Bei Yu}
\end{itemize}

% \subsection{The Chinese University of Hong Kong}[Hong Kong]
\begin{positions}
  \entry{M.Sc.\ in Computer Science}{Nov 2019~--~Feb 2020}
\end{positions}
\vspace{-\parskip}%
\begin{itemize}
  \item Advisor: \href{http://www.cse.cuhk.edu.hk/~byu/}{Prof.~Bei Yu}
  % \item  \printdate{}
  % \item Dissertation: \href{https://repository.hkbu.edu.hk/etd_oa/620}{Authenticated Query Processing in the Cloud}
\end{itemize}

\subsection{Huazhong University of Science and Technology}[Wuhan, China]
\begin{positions}
  \entry{Bachelor of Computer Science}{Sep 2015~--~Jun 2019}
\end{positions}
\vspace{-\parskip}%
% \begin{itemize}[label={}]
%   \item  \printdate{}
% \end{itemize}

\section{Skills}

\begin{description}
  \item[Programming] C/C++, Rust, Java, Python, Ruby, Matlab, \LaTeX, Bash, Javascript
  \item[Tools] Vim, Tmux, Git, macOS, Linux
  \item[Languages] English, Mandarin
\end{description}

\section{Publications}%

\publications{publications.bib}

\section{Talks}

\begin{enumerate}
  \item Blockchain Privacy Preserving Techniques, \emph{The 36th CCF National Database Conference}, Jinan, China, Oct.~2019.
  \item Towards Searchable and Verifiable Blockchain, \emph{1st Workshop on Blockchain and Data Management at 35th IEEE International Conference on Data Engineering}, Macau, Apr.~2019.
  \item When Query Authentication Meets Fine-Grained Access Control: A Zero-Knowledge Approach, \emph{2018 ACM SIGMOD International Conference on Management of Data}, Houston, USA, Jun.~2018.
\end{enumerate}

\section{Awards}

\begin{itemize}
  \item SIGMOD Travel Award, ACM \printdate{2018}
  \item Department RPg Performance Award, Hong Kong Baptist University \printdate{2018,~2019}
  \item Postgraduate Research Symposium Best Research Performance Award \& Best Poster Award, Hong Kong Baptist University \printdate{2018}
  \item Yakun Scholarship Scheme for Mainland Postgraduate Students, Hong Kong Baptist University \printdate{2018}
  \item Excellent Teaching Assistant Performance Award, Hong Kong Baptist University \printdate{2017}
  \item Teaching Assistant Performance Award, Hong Kong Baptist University \printdate{2015,~2016}
\end{itemize}

\end{document}
